---
title: "Advanced Analytics for Web"
output:
  html_document:
    toc_float: false
    includes:
      before_body: [includes/navbar.html, includes/navbar_left.html]

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Welcome to the Advanced Analytics for Web accelerator. In this guide you'll learn how to set up tracking and enrichment as well as how to model and visualise Snowplow data. 

Once finished, you will be able to build a deeper understanding of customer behavior on your website and use your data to influence business decisions.

***

### Who is this guide for?
Data practicioners with or without Javascript developer experience who would like to set up tracking on their company's website and learn how to use the out of the box snowplow web data modelling so that they can gain insight of their customers' behavioural data as quick as possible.

***

### What you'll learn

- **Track-** Setup and deploy tracking to your web app
- **Enrich-** Add enrichments to your data
- **Model-** Configure the snowplow-web data model and run it against your Snowflake warehouse
- **Visualise-** Visualise your output data with Streamlit 

```{r, echo = FALSE}

mermaid("
                gantt 
                dateFormat H HH
                section 1. Track
                8h          :tracking, 0, 8h
                section 2. Enrich
                4h            :enrich, after tracking, 4h
                section 3. Model
                2h          :model, after enrich, 2h
                section 4. Visualise
                5h            :visaualise, after model, 5h
                ")
```


***

### Prerequisites
- Snowplow Pipeline
- Web app to implement tracking on
- dbt installed
  - a new dbt project created and configured
  - a dataset of web events from the Snowplow Javascript tracker in your data warehouse (Snowflake will be used for illustration but the package also supports BigQuery, Databricks, Postgres and Redshift)


